---
title: "linear_models"
author: "Anyu Zhu"
date: "11/16/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

Load NYC airbnb data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group
  ) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighbourhood, room_type)
```

Visualizations

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```

## Fit a linear model

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
fit
summary(fit)
fit %>% broom::tidy()
```

```{r}
fit %>% 
  broom :: tidy() %>% 
  mutate(term = str_replace(term, "borough", "Borough: ")) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

## Diagnostic

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = resid)) +
  geom_density() +
  xlim(-200, 200)
```

## Interactions, nesting

```{r}
fit = lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)

broom::tidy(fit)
```

```{r}
nyc_airbnb %>% 
  relocate(borough) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    lm_results = map(lm_fits, broom::tidy)
  ) %>% 
  select(borough, lm_results) %>% 
  unnest(lm_results) %>% 
  filter(term == "stars")
```

neighborhoods in Manhattan
```{r}
manhattan_lm_results_df = nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  select(-borough) %>% 
  relocate(neighbourhood) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    lm_results = map(lm_fits, broom::tidy)
  ) %>% 
  select(neighbourhood, lm_results) %>% 
  unnest(lm_results)

manhattan_lm_results_df %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) +
  geom_density()

manhattan_lm_results_df %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighbourhood, y = estimate)) +
  geom_point() +
  facet_grid(~term) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Logistic Regression

for binary outcome

```{r}
nyc_airbnb = nyc_airbnb %>% 
  mutate(
    expensive_apt = as.numeric(price > 500)
  )

logistic_fit = 
  glm(expensive_apt ~ stars + borough,
    data = nyc_airbnb, 
    family = binomial())

logistic_fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: "),
    estimate = exp(estimate)
  ) %>% 
  select(term, OR = estimate, p.value)

nyc_airbnb %>% 
  modelr::add_predictions(logistic_fit) %>% 
  mutate(pred = boot::inv.logit(pred)) # get probabilities of 0 or 1
```

## Cross Validation

```{r}
library(modelr)
library(mgcv)
```

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

Create splits by hand

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) +
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

fit my models 

```{r}
linear_mod = lm(y ~x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~s(x, k = 30), sp = 10e-6, data = train_df)
```

plot the results

```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred))

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred))
```

quantify the results

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

## CV iteratively
```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

fit some models
```{r}
cv_df = cv_df %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~gam(y ~ x, data = .x)),
    wiggly_mod = map(.x = train, ~gam(y ~s(x, k = 30), sp = 10e-6, data = train_df))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test,~ rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_mod, .y = test,~ rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x = wiggly_mod, .y = test,~ rmse(model = .x, data = .y))
  )
```

look at output

```{r}
cv_df %>% 
  select(.id, starts_with("rmse")) %>% 
  pivot_longer(
    rmse_linear:rmse_wiggly,
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

## Child growth data

```{r}
child_growth = read_csv("nepalese_children.csv") %>% 
  mutate(
    weight_cp = (weight > 7) * (weight - 7)
  )
```

```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .2)
```

Consider a linear model first 

```{r}
linear_mod = lm(armc ~ weight, data = child_growth)
pwl_mod = lm(armc ~ weight + weight_cp, data = child_growth)
smooth_mod = gam(armc ~ s(weight), data = child_growth)
```

```{r}
child_growth %>% 
  add_predictions(pwl_mod) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = 0.2) +
  geom_line(aes(y = pred), color = "red")
```

Use CV to compare models

```{r}
cv_df = 
  crossv_mc(child_growth, 100) %>% 
  mutate(
    linear_mod  = map(train, ~lm(armc ~ weight, data = .x)),
    pwl_mod     = map(train, ~lm(armc ~ weight + weight_cp, data = .x)),
    smooth_mod  = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))
  ) %>% 
   mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_pwl    = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)))
```

Look at rmse

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_boxplot()
```

